Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation

### 2022-03-29 Response_Letter/Response_Letter.tex

However general conclusions like "BSE@GT performs best for few-electron systems whereas BSE@GW is better for larger systems" 
are drawn out of only 3 systems: H2, H2O and BeH2. None of the 3 can be considered as a "large" system.

I think the work would be much stronger with a more comprehensive benchmark set.}
\\
\alert{
We thanks the reviewer for these positive comments.
We are planning on performing a comprehensive benchmark in a forthcoming paper but we feel that it is currently outside the scope of the present paper which is dedicated to the introduction of a new theory and test calculations.
Accordingly to the reviewer's comment, we have soften our conclusion about the accuracy of BSE@GT for large systems while mentioning that a more comprehensive benchmark study would be required:
``The overall accuracy of the present scheme still needs to be assessed for larger systems (where the screening is known to be more important). 
For such purposes, a comprehensive benchmark study would be required and we are planning to do so in the future''
}

\begin{enumerate}

\item 
{Eq. (3) shows the non-interacting Green's function. 
The word "non-interacting" is missing in the text (else $i$ and $a$ are not orbital indices). }
\\
\alert{The referee is correct, Eq.~3 is not the fully interacting Green's function with the notation used in the manuscript. 
To avoid confusion with the non-interacting Green's function, which usually refers to the case where the electron-electron interaction is switched off, we have now added to the manuscript that Eq.~3 is the Green's function within the quasiparticle approximation, meaning that it is built from one-electron energies and orbitals corresponding to a given electronic structure method, such as Hartree-Fock, Kohn-Sham, or $GW$ (retaining only the quasiparticle part). We have hence changed the text before Eq. 3 as "By definition, in the quasiparticle approximation, the one-body Green's function is".
}

@@

\item 
{In Eq. (23), the block $B^\text{BSE}$ should not have a dependence wrt $\Omega_S$ to be consistent with Eq. (20).}
\\
\alert{
Thank you for spotting this typo. 
This has been corrected.
}

\item 
{In Figs. 2 \& 5, some curves are hidden behind other curves. For instance the G0W0 LUMO is virtually impossible to distinguish. 
Having HOMO, LUMO and the band gap on the same plot is maybe not a good representation.}
\\
\alert{
We have improved Figs.~2 and 5 and we plot separately these three quantities.
}

\item 
{The GT self-energy in Eq. (12) is very different from the GW self-energy. 
But according to Fig 2 and 5, the quasiparticle energies are very similar. 
Is it something that expected? 
Are all the GW diagrams included in the the GT self-energy?}
\\
\alert{The $T$-matrix self-energy contains all the diagrams of the $GW$ self-energy up to second order in the bare Coulomb interaction (this means the Hartree-Fock self energy and the second order direct term). 
At higher order, the two approximations differ, since, as mentioned in the manuscripts, $GW$ contains the so-called bubble diagrams and the $T$-matrix the ladder diagrams. 
Probably the fact that both approximations give similar quasiparticle energies for the small systems we study in the manuscript is due to the fact that the second-order diagrams are the most important ones in this case. 
As already mentioned in the manuscript, this trend has already been observed in the Hubbard dimer and in molecular systems. 
We should also mention that in the case of the Hubbard dimer, the two approximations do not give similar satellite energies and amplitudes. 
Hence, it is difficult to draw conclusions on the observed trends.}

### 2022-03-29 Manuscript/Tmatrix.tex
adding references

Alternatives to $GW$ do exist. For example, the $T$-matrix (or Bethe-Goldstone) approximation, first introduced in nuclear physics, \cite{Bethe_1957,Baym_1961,Baym_1962,Danielewicz_1984a,Danielewicz_1984b} then in condensed matter physics, \cite{Liebsch_1981,Bickers_1989,Bickers_1991,Katsnelson_1999,Katsnelson_2002,Zhukov_2005,vonFriesen_2010,Romaniello_2012,Gukelberger_2015} and more recently in quantum chemistry, \cite{Zhang_2017,Li_2021b} sums to infinity the ladder diagrams from the particle-particle (pp) channel and is justified in the low-density or strongly-correlated regime. \cite{Danielewicz_1984a,Danielewicz_1984b,Liebsch_1981,Shepherd_2014}
While the two-point screened interaction $W$ is the cornerstone of $GW$, the $T$-matrix approximation relies on a more complex (four-point) effective interaction --- the so-called $T$ matrix --- yielding the following self-energy: 
\begin{equation}
\label{eq:SigGT}
	\Sigma^{GT}(1,2) = i \int G(4,3) T(1,3;2,4) d3 d4
\end{equation}
The natural idea of combining the ph and pp channels is also possible and has been explored, for example, in the Hubbard dimer within many-body perturbation theory (see Ref.~\onlinecite{Romaniello_2012} and references therein) and the uniform electron gas \cite{Loos_2016} within coupled-cluster theory. \cite{Shepherd_2014}

>>>>

Alternatives to $GW$ do exist. For example, the $T$-matrix (or Bethe-Goldstone) approximation, first introduced in nuclear physics, \cite{Bethe_1957,Baym_1961,Baym_1962,Danielewicz_1984a,Danielewicz_1984b} then in condensed matter physics, \cite{Liebsch_1981,Bickers_1989,Bickers_1991,Katsnelson_1999,Katsnelson_2002,Zhukov_2005,vonFriesen_2010,Romaniello_2012,Gukelberger_2015,Muller_2019,Friedrich_2019,Biswas_2021} and more recently in quantum chemistry, \cite{Zhang_2017,Li_2021b} sums to infinity the ladder diagrams from the particle-particle (pp) channel and is justified in the low-density or strongly-correlated regime. \cite{Danielewicz_1984a,Danielewicz_1984b,Liebsch_1981,Shepherd_2014}
While the two-point screened interaction $W$ is the cornerstone of $GW$, the $T$-matrix approximation relies on a more complex (four-point) effective interaction --- the so-called $T$ matrix --- yielding the following self-energy: 
\begin{equation}
\label{eq:SigGT}
	\Sigma^{GT}(1,2) = i \int G(4,3) T(1,3;2,4) d3 d4
\end{equation}
The natural idea of combining the ph and pp channels is also possible and has been explored, for example, in the Hubbard dimer within many-body perturbation theory (see Ref.~\onlinecite{Romaniello_2012} and references therein) and the uniform electron gas \cite{Loos_2016} within coupled-cluster theory. \cite{Shepherd_2014}
